### 2016-05-20 Paper_v1.tex
May20

\subsection*{Calculation of CAT yield}
The yield on CAT production was calculated for three cases: the experimental data, the best-fit parameter set, and a theoretical maximum yield.
In each case the yield was formulated as a ratio of carbon produced as CAT to carbon consumed as reactants (glucose and amino acids):
\begin{equation}\label{eqn:yield-definition}
	Yield=\frac{\Delta CAT\;C_{CAT}}{\sum_{i=1}^{\mathcal{R}}\max(\Delta m_{i},0)\;C_{m_i}}
\end{equation}
where $\Delta CAT$ denotes the amount of CAT produced, $C_{CAT}$ denotes carbon number of CAT, $\mathcal{R}$ denotes the number of reactants, $\Delta m_{i}$ denotes the amount of the $i$th reactant consumed, never allowed to be negative, and $C_{m_i}$ denotes the carbon number of the $i$th reactant.
Because no data was available for arginine or glutamate, these reactants were left out of all three calculations.
In the experimental case and the best-fit set case, yield was calculated by setting $\Delta CAT$ equal to the final minus the initial CAT concentration and setting $\Delta m_{i}$ equal to the initial minus the final reactant concentration.
The theoretical yield was calculated using flux balance anaylsis (FBA) with a sequence-based analysis on CAT.
The sequence specific FBA \cite{2002_allen_palsson} problem was formulated as:
\begin{equation}\label{eqn:FBA}
\begin{split}
	\max_{\boldsymbol{v}}{} \! \left( v_{obj}=\mathbf{\boldsymbol{c}}^T \boldsymbol{v} \right) \qquad \alpha_i \leq v_i \leq \beta_i  \qquad i=1,2,\hdots,\mathcal{R} \\
	\mathrm{Subject \; to:}	\; \; \mathbf{S}\mathbf{v}=\mathbf{0}\qquad\qquad\qquad\qquad\qquad\qquad\qquad\quad
\end{split}
\end{equation}
where $\mathbf{S}$ denotes the stoichiometric matrix, $\mathbf{v}$ denotes the unknown flux vector, $\boldsymbol{c}$ denotes the objective selection vector, and $\alpha_i$ and $\beta_i$ denote the lower and upper bounds on flux $v_{i}$, respectively.
The stoichiometric matrix was expanded to include the transcription and translation reactions for producing CAT. 
The objective $v_{obj}$ was to maximize the specific rate of CAT formation.
The specific glucose, amino acids and oxygen uptake rates were constrained to allow a maximum flux of 10 mM/hr.
The flux balance analysis problem was solved using the GNU Linear Programming Kit (v4.52) \cite{GLPK}.
The solution flux vector was used to calculate the theoretical carbon yield of CAT, reformulated in terms of flux:
\begin{equation}\label{eqn:yield}
	Yield=\frac{v_{CAT}\;C_{CAT}}{\sum_{i=1}^{\mathcal{R}}\max(v_{i},0)\;C_{i}}
\end{equation}
where $v_{CAT}$ denotes the CAT export flux and $v_{i}$ denotes the import flux of the $i$th substrate.

>>>>

\subsection*{Calculation of CAT yield}
The yield on CAT production was calculated for three cases: the experimental data, the best-fit parameter set, and a theoretical maximum yield.
In each case the yield was formulated as a ratio of carbon produced as CAT to carbon consumed as reactants (glucose and amino acids):
\begin{equation}\label{eqn:yield-definition}
	Yield=\frac{\Delta CAT\;C_{CAT}}{\sum_{i=1}^{\mathcal{R}}\max(\Delta m_{i},0)\;C_{m_i}}
\end{equation}
where $\Delta CAT$ denotes the amount of CAT produced, $C_{CAT}$ denotes carbon number of CAT, $\mathcal{R}$ denotes the number of reactants, $\Delta m_{i}$ denotes the amount of the $i$th reactant consumed, never allowed to be negative, and $C_{m_i}$ denotes the carbon number of the $i$th reactant.
Because no data was available for arginine or glutamate, these reactants were left out of all three calculations.
In the experimental case and the best-fit set case, yield was calculated by setting $\Delta CAT$ equal to the final minus the initial CAT concentration and setting $\Delta m_{i}$ equal to the initial minus the final reactant concentration.
The theoretical yield was calculated using flux balance anaylsis (FBA) with a sequence-based analysis on CAT.
The sequence specific FBA \cite{2002_allen_palsson} problem was formulated as:
\begin{equation}\label{eqn:FBA}
\begin{split}
	\max_{\boldsymbol{v}}{} \! \left( v_{obj}=\mathbf{\boldsymbol{c}}^T \boldsymbol{v} \right) \qquad \alpha_i \leq v_i \leq \beta_i  \qquad i=1,2,\hdots,\mathcal{R} \\
	\mathrm{Subject \; to:}	\; \; \mathbf{S}\mathbf{v}=\mathbf{0}\qquad\qquad\qquad\qquad\qquad\qquad\qquad\quad
\end{split}
\end{equation}
where $\mathbf{S}$ denotes the stoichiometric matrix, $\mathbf{v}$ denotes the unknown flux vector, $\boldsymbol{c}$ denotes the objective selection vector, and $\alpha_i$ and $\beta_i$ denote the lower and upper bounds on flux $v_{i}$, respectively.
The stoichiometric matrix was expanded to include the transcription and translation reactions for producing CAT. 
The objective $v_{obj}$ was to maximize the specific rate of CAT formation.
The specific glucose uptake rate was constrained to allow a maximum flux of 10 mM/hr \cite{2002_Mahadevan_BiophysJ}; the amino acids and oxygen uptake rates were also bound to allow a maximum flux of 10 mM/hr, but did not reach this maximum flux.
Glucose, oxygen, and amino acids were modeled as being imported into the system, whereas CAT synthesis was modeled through protein export.
The rest of the network followed a psuedo steady-state asusmption where all other metabolites were not allowed to accumulate; thus, the network could be solved by linear programming. 
The flux balance analysis problem was solved using the GNU Linear Programming Kit (v4.52) \cite{GLPK}.
The solution flux vector was used to calculate the theoretical carbon yield of CAT, reformulated in terms of flux:
\begin{equation}\label{eqn:yield}
	Yield=\frac{v_{CAT}\;C_{CAT}}{\sum_{i=1}^{\mathcal{R}}\max(v_{i},0)\;C_{i}}
\end{equation}
where $v_{CAT}$ denotes the CAT export flux and $v_{i}$ denotes the import flux of the $i$th substrate.
